\section{At present my favourite gadgets}
Modern age is an age of science and technology. Modern technology is a great blessing for mankind. We can not think for our modern life without technology. The use of technology has made our life easy and comfortable.  Modern civilization is the gift of technology. Radio, television, computer, refrigerator, dish-antena etc are the blessing of modern technology.\\
\subsection{At present mobile phone} Mobile makes the world easier.If we consider mobile phone, then we see a lot of changes occurs itself. In the early of invention of mobile it was so large and it was attached to wire. But the welfare of science and technology wireless cell phone was released. So it was easy to carry it with anyone at any places. Thus new version of mobile phone is released one after another. And in a smart phone is published. This is an absolutely great achievement for people. By using these mobile phone any one can access internet and can communicate with others via internet. Now-a-days some new features is added to smart phone such as finger print and face detection. Another important feature is high resolution camera. At past we would depend on camera devices for best photo but now we can have the best photo using smart phone.
\subsection{At present computer}
At the beginning of the invention of computer, the shape of computer was so large shown in figure~\ref{fig:fig4}. That computer possessed the volume of a small room. In ~\cite{www.geeksforgeeks.org}, www.geeksforgeeks.orgWebsite, provided that the processor of the first generation computer was made by vacuum tubes.\\In second generation computer, transistors were used to make processor. Another feature was the core storage. A transistor may be a device composed of semiconductor material that amplifies a sign or opens or closes a circuit.\\ During the third generation, technology envisaged a shift from huge transistors to integrated circuits, also referred to as IC. \\
In 1971 First microprocessors were used, the large scale of integration LSI circuits built on one chip called microprocessors. The most advantage of this technology is that one microprocessor can contain all the circuits required to perform arithmetic, logic, and control functions on one chip.\\
The technology behind the fifth generation of computers is AI. It allows computers to behave like humans. It is often seen in programs like voice recognition, area of medicines, and entertainment. Within the field of games playing also it’s shown remarkable performance where computers are capable of beating human competitors.\\
The speed is highest, size is that the smallest and area of use has remarkably increased within the fifth generation computers. Though not a hundred percent AI has been achieved to date but keeping in sight the present developments, it is often said that this dream also will become a reality very soon. Thus now twelveth 

